General constraints on magic distillation protocols from statistical mechanics

### 2021-06-05 magic_paper.tex
added on explanation of even/odd working, corrected mistakes ontheorem bridging H_a and D_a

% Notation consistency (R is rate not bound, noise vs error, \ln{} -> \ln, italics)
% UK vs US english
% Spacing (figs, sections, paragraphs, eq. numbering, \noindent, QEDs)

@@

One prominent magic monotone is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)},
\end{equation}
where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
\begin{equation}
    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
\end{equation}

@@

The first elbow coordinates for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by considering the slope of the line segment joining this first elbow to the origin we can use~\cref{prop:first_elb} in the Appendices, to bound $R(\epsilon, \epsilon')$. We find that
\begin{equation}
	R(\epsilon, \epsilon') \leq \frac{\ln{(3-4\epsilon)}}{\ln{(3-4\epsilon')}}.
\end{equation}
For the limiting case of pure magic states on the output ($\epsilon'=0$), this simplifies to
\begin{equation}
	R \leq 1 + \frac{\ln (1 - \frac{4}{3} \epsilon)}{\ln 3}.
\end{equation}
This can be compared to other known distillation bounds coming from mana and thauma~\cite{Wang_2020}. The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
\end{equation}
The recently introduced max--thauma~\cite{Wang_2020} is defined as
\begin{equation}
	\theta_{\rm{max}}(\rho) \coloneqq \log_2{\min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}}
\end{equation}
and can be calculated numerically via a semi-definite program. For the noisy Strange state, the max--thauma bound coincides with the mana bound, and we find that they are both looser than the majorization bound we derived via the first elbow constraint as shown in~\cref{fig:distill_bounds}.

@@

Then the asymptotic magic distillation rate $R = m/n$ is bounded as
\begin{equation}\label{eq:rate_bounds_proof}
	R \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
\end{equation}
where $F$ is the free energy of $\tau$,  and 
\begin{equation}
	\phi = -\beta^{-1} \log \zeta
\end{equation}
with $\zeta$ given by the expressions
\begin{align}
	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
	\alpha_k &= \<E_k| A_{\x_\star} |E_k\>,
\end{align}
and $W_\tau(\x)$ attaining a minimum at $\x=\x_\star$. The primed variables are defined similarly for the output system.
\end{theorem}
\noindent The proof of this is provided in~\cref{thm:free-energy-bound-proof}, and follows a similar line as taken for our unital protocol bound.

@@

Since the magic monotone mana is a monotonic function of sum-negativity, $\rm{mana}(\rho) \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)}$, we see that mana corresponds precisely to the peak of the Lorenz curve $L_{\rho|\sigma}(x)$. Therefore, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any fragment.
\end{proof}

@@

We then prove the following result connecting simple majorization to relative majorization.
\nick{move following lemma to section on relative majorization equivalent conditions}
\begin{lemma}
Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$. 
Then,
\begin{equation}
(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
\end{equation}
where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
\begin{equation}
	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{b_i},
\end{equation}
with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
\end{lemma}
\begin{proof}
	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
\begin{equation}
	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
\end{equation}
that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\x) = \x$ for all $\x \in \mathbb{R}^N$.

@@

Given a fixed $\alpha$ for which $H_\alpha(\x)$ is well-defined, the function $H_\alpha$ is real-valued, smooth on the interior of $\mathcal{Q}^\downarrow$ and symmetric on permutation components of $\x$.

Consider the partial derivatives
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}(-w_i^{\alpha-1}).
\end{equation}
We first note that for $\alpha$ in the given form, it is always true that
\begin{equation}
	\frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}} > 0.
\end{equation}
We then show that for $\alpha$ in the given form, the function $f(w) = -w^{\alpha - 1}$ is non-increasing.
To this end, we obtain the first derivative
\begin{equation}
	f'(w) = -(\alpha - 1) w^{\alpha-2} = -(\alpha - 1)w^{\frac{2a-4b+2}{2b-1}} \leq 0,
\end{equation}
because $\alpha > 1$ and
\begin{equation}
	w^{\frac{2a-4b+2}{2b-1}} = \left(w^{2a-4b+2}\right)^{\frac{1}{2b-1}} = \left(w^{\frac{1}{2b-1}}\right)^{2(a-2b+1)} \geq 0,
\end{equation}
where each expression is well defined because the rational exponent has even numerator and odd denominator.
\nick{This step is the reason why $\alpha =$ odd$/$odd or $\alpha < 1$ do not work. $\alpha - 2$ may be less than 0, is this a problem?}

Therefore, whenever $w_i \geq w_j$, we have that 
\begin{equation}
	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
\end{equation}
which leads to
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} \leq \frac{\partial H_\alpha}{\partial w_j}.
\end{equation}
Therefore, $H_\alpha$ is Schur-concave and
\begin{equation}
	H_\alpha(\w) \leq H_\alpha(\w'),
\end{equation}
for any quasi-distributions $\w, \w'$.

\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|c||c|c}
    $w_i$ & $w_{i+1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ \\[0.5ex]\hline
    $2$ & $1.5$  & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
    $2$ & $-1.5$ & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
    $2$ & $-2.5$ & $3$ & $2 < 3.125$ F & $1/3$ & $-0.94 < -0.81$ F \\[0.5ex]\hline
    $2/3$ & $1/3$  & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
    $2/3$ & $-1/3$ & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
    $2/3$ & $-4/3$ & $3$ & $0.22 < 0.89$ F & $1/3$ & $-1.97 < -1.24$ F \\[0.5ex]\hline
    $2$ & $1.5$  & $4$ & $2.67 > 1.125$ T & $2/3$ & $-2.38 > -2.62$ T \\
    $2$ & $-1.5$ & $4$ & $2.66 > -1.125$ T & $2/3$ & $-2.38 > 2.62$ F \\
    $2$ & $-2.5$ & $4$ & $2.66 > 5.21$ T & $2/3$ & $-2.38 > 2.21$ F \\
    $-2$ & $-2.5$ & $4$ & $-2.66 > -5.21$ T & $2/3$ & $2.38 > 2.21$ T \\[0.5ex]\hline
    $2/3$ & $1/3$  & $4$ & $0.10 > 0.01$ T & $2/3$ & $-3.43 > -4.33$ T \\
    $2/3$ & $-1/3$ & $4$ & $0.10 > -0.01$ T & $2/3$ & $-3.43 > 4.33$ F \\
    $2/3$ & $-4/3$ & $4$ & $0.10 > -0.79$ T & $2/3$ & $-3.43 > 2.73$ F \\
    $-1/3$ & $-2/3$ & $4$ & $-0.01 > -0.10$ T & $2/3$ & $4.33 > 3.43$ T \\
    $-1/3$ & $-4/3$ & $4$ & $-0.01 > -0.79$ T & $2/3$ & $4.33 > 2.73$ T
  \end{tabular}
  \caption{\nick{NUMERICS ON SCHUR-OSTROWSKI CONDITION} Seems like $\alpha=$ even$/$odd and $\alpha > 1$ works for any combination of $w_i, w_{i+1}$ with $w_i > w_{i+1}$ and seems also that no other case works.}
  \label{tab:test}
\end{table}

\end{proof}
Note that if $\alpha < 1$ or is of the form odd$/$even, the argument of~\cref{thm:HSchur} does not hold.
However, the set $F := \{2a/(2b+1): a,b \in \mathbb{N} \text{ and } a>b\}$ is dense in the rationals $\mathbb{Q}_{>1}$ (which in turn is dense in $\mathbb{R}_{>1}$) as any rational $c/d$ with $c>d$ can be approximated by a sequence $f_n := c2^n / (d2^n+1)$ with every element $f_n$ in the set $F$. \nick{can turn into lemma}

@@

\begin{theorem}
	Consider a general magic state distillation process that converts magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes n'}$ as well as equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes n'}$, where we assume that $W_{\tau^{\otimes n}}(\bmx) = a_{\bmx}/K$ and $W_{\tau'^{\otimes n'}}(\bmx) = a_{\bmx}/K$ for positive integers $a_{\bmx}, a_{\bmx}'$ and $K = \sum_{\bmx} a_{\bmx} = \sum_{\bmx} a_{\bmx}'$.

@@

	We have that $(W_{\rho_n}, W_{\tau_n}) \succ W_{\rho'_{n'}}, W_{\tau'_{n'}})$, or equivalently $\Gamma_{\bma}(W_{\rho_n}) \succ \Gamma_{\bma'}(W_{\rho'_{n'}})$, where
\begin{align}
	\Gamma_{\bma}(W_{\rho_n}) &= \bigoplus_{\bmx} W_{\rho_n}(\bmx) \left(\frac{1}{KW_{\tau_n}(\bmo)}, \dots, \frac{1}{KW_{\tau_n}((d,d))} \right)\nonumber\\
	&= \frac{1}{K}\bigoplus_{\bmx}\bigoplus_{\bmy} \frac{W_{\rho_n}(\bmx)}{W_{\tau_n}(\bmy)},
\end{align}
and similarly for $\Gamma_{\bma'}(W_{\rho'_{n'}})$.
Therefore,
\begin{equation}
	H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) = \frac{1}{1-\alpha} \log_2 \left( \frac{1}{K^\alpha} \sum_{\bmx, \bmy} \frac{W_{\rho_n}(\bmx)^\alpha}{W_{\tau_n}(\bmy)^\alpha} \right),
\end{equation}
while
\begin{equation}
	D(\rho||\tau) = \frac{1}{\alpha-1} \log_2 \sum_{\bmx,\bmy} \frac{W_{\rho}(\bmx)^\alpha}{W_{\tau}(\bmy)^{\alpha-1}}.
\end{equation}
\nick{correct mistakes, bridge gaps}
\end{proof}

>>>>

% Notation consistency (R is rate not bound, noise vs error, \ln{} -> \ln, italics, keep \bmx for vectors?)
% UK vs US english
% Spacing (figs, sections, paragraphs, eq. numbering, \noindent, QEDs)

@@

One prominent magic monotone is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \ln (2\hspace{1pt}\sn{\rho}+1),
\end{equation}
where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
\begin{equation}
    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
\end{equation}

@@

The first elbow coordinates for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by considering the slope of the line segment joining this first elbow to the origin we can use~\cref{prop:first_elb} in the Appendices, to bound $R(\epsilon, \epsilon')$. We find that
\begin{equation}
	R(\epsilon, \epsilon') \leq \frac{\ln (3-4\epsilon)}{\ln (3-4\epsilon')}.
\end{equation}
For the limiting case of pure magic states on the output ($\epsilon'=0$), this simplifies to
\begin{equation}
	R \leq 1 + \frac{\ln (1 - \frac{4}{3} \epsilon)}{\ln 3}.
\end{equation}
This can be compared to other known distillation bounds coming from mana and thauma~\cite{Wang_2020}. The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
\end{equation}
The recently introduced max--thauma~\cite{Wang_2020} is defined as
\begin{equation}
	\theta_{\rm{max}}(\rho) \coloneqq \log_2{\min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}}
\end{equation}
and can be calculated numerically via a semi-definite program. For the noisy Strange state, the max--thauma bound coincides with the mana bound, and we find that they are both looser than the majorization bound we derived via the first elbow constraint as shown in~\cref{fig:distill_bounds}.

@@

Then the asymptotic magic distillation rate $R = m/n$ is bounded as
\begin{equation}\label{eq:rate_bounds_proof}
	R \leq \dfrac{\ln \big( 1-\frac{4}{3}\epsilon \big) + \beta (\phi - F)}{\ln \big( 1-\frac{4}{3}\epsilon' \big) + \beta (\phi' - F')},
\end{equation}
where $F$ is the free energy of $\tau$,  and 
\begin{equation}
	\phi = -\beta^{-1} \log \zeta
\end{equation}
with $\zeta$ given by the expressions
\begin{align}
	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
	\alpha_k &= \<E_k| A_{\x_\star} |E_k\>,
\end{align}
and $W_\tau(\x)$ attaining a minimum at $\x=\x_\star$. The primed variables are defined similarly for the output system.
\end{theorem}
\noindent The proof of this is provided in~\cref{thm:free-energy-bound-proof}, and follows a similar line as taken for our unital protocol bound.

@@

Since the magic monotone mana is a monotonic function of sum-negativity, $\rm{mana}(\rho) \coloneqq \ln \hspace{1pt}(2\hspace{1pt}\sn{\rho}+1)$, we see that mana corresponds precisely to the peak of the Lorenz curve $L_{\rho|\sigma}(x)$. Therefore, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any fragment.
\end{proof}

@@

We then prove the following result connecting simple majorization to relative majorization.
\nick{move following lemma to section on relative majorization equivalent conditions}
\begin{lemma}
Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$. 
Then,
\begin{equation}
(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
\end{equation}
where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
\begin{equation}
	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{a_i},
\end{equation}
with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
\end{lemma}
\begin{proof}
	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
\begin{equation}
	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
\end{equation}
that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\x) = \x$ for all $\x \in \mathbb{R}^N$.

@@

Given a fixed $\alpha$ for which $H_\alpha(\x)$ is well-defined, the function $H_\alpha$ is real-valued, smooth on the interior of $\mathcal{Q}^\downarrow$ and symmetric on any component permutation of $\x$.

Consider the partial derivatives
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}(-w_i^{\alpha-1}).
\end{equation}
We first note that for $\alpha$ in the given form, it is always true that
\begin{equation}
	\frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}} > 0.
\end{equation}
We then show that for $\alpha$ in the given form, the function $f(w) = -w^{\alpha - 1}$ is non-increasing.
To this end, we first note that, for $\alpha > 1$, $f(w)$ has no discontinuities and we then obtain the first derivative
\begin{equation}
	f'(w) = -(\alpha - 1) w^{\alpha-2} = -(\alpha - 1)w^{\frac{2a-4b+2}{2b-1}} \leq 0,
\end{equation}
because $\alpha > 1$ and
\begin{equation}
	w^{\frac{2a-4b+2}{2b-1}} = \left(w^{2a-4b+2}\right)^{\frac{1}{2b-1}} = \left(w^{\frac{1}{2b-1}}\right)^{2(a-2b+1)} \geq 0,
\end{equation}
where each expression is well-defined because the rational exponent has odd denominator.

\nick{This step is the reason why $\alpha =$ odd$/$odd or $\alpha < 1$ do not work.

Example 1: if $\alpha =$ odd$/$odd, then $f(w)$ is not monotonous because the sign of $f'(w)$ would depend on the sign of $w$. 
In~\cref{tab:test}, this case fails when $w_i > 0 > -w_i > w_{i+1}$.

Example 2: if $\alpha =$ even$/$odd and $\alpha < 1$, then  $f(w)$ is not monotonous across $0$ because and in fact $\lim_{w\rightarrow 0^+} f(w) = -\infty$, while $\lim_{w\rightarrow 0^-} f(w) = +\infty$. 
In~\cref{tab:test}, this case fails when $w_i > 0 > w_{i+1}$.
}

Therefore, whenever $w_i \geq w_j$, we have that 
\begin{equation}
	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
\end{equation}
which leads to
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} \leq \frac{\partial H_\alpha}{\partial w_j}.
\end{equation}
Therefore, $H_\alpha$ is Schur-concave and
\begin{equation}
	H_\alpha(\w) \leq H_\alpha(\w'),
\end{equation}
for any quasi-distributions $\w, \w'$ that obey $\w \succ \w'$.

\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|c||c|c}
    $w_i$ & $w_{i+1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ \\[0.5ex]\hline
    $2$ & $1.5$  & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
    $2$ & $-1.5$ & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
    $2$ & $-2.5$ & $3$ & $2 < 3.125$ F & $1/3$ & $-0.94 < -0.81$ F \\[0.5ex]\hline
    $2/3$ & $1/3$  & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
    $2/3$ & $-1/3$ & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
    $2/3$ & $-4/3$ & $3$ & $0.22 < 0.89$ F & $1/3$ & $-1.97 < -1.24$ F \\[0.5ex]\hline
    $2$ & $1.5$  & $4$ & $2.67 > 1.125$ T & $2/3$ & $-2.38 > -2.62$ T \\
    $2$ & $-1.5$ & $4$ & $2.66 > -1.125$ T & $2/3$ & $-2.38 > 2.62$ F \\
    $2$ & $-2.5$ & $4$ & $2.66 > 5.21$ T & $2/3$ & $-2.38 > 2.21$ F \\
    $-2$ & $-2.5$ & $4$ & $-2.66 > -5.21$ T & $2/3$ & $2.38 > 2.21$ T \\[0.5ex]\hline
    $2/3$ & $1/3$  & $4$ & $0.10 > 0.01$ T & $2/3$ & $-3.43 > -4.33$ T \\
    $2/3$ & $-1/3$ & $4$ & $0.10 > -0.01$ T & $2/3$ & $-3.43 > 4.33$ F \\
    $2/3$ & $-4/3$ & $4$ & $0.10 > -0.79$ T & $2/3$ & $-3.43 > 2.73$ F \\
    $-1/3$ & $-2/3$ & $4$ & $-0.01 > -0.10$ T & $2/3$ & $4.33 > 3.43$ T \\
    $-1/3$ & $-4/3$ & $4$ & $-0.01 > -0.79$ T & $2/3$ & $4.33 > 2.73$ T
  \end{tabular}
  \caption{\nick{NUMERICS ON SCHUR-OSTROWSKI CONDITION} The case $\alpha=$ even$/$odd and $\alpha > 1$ works for any combination of $w_i, w_{i+1}$ with $w_i > w_{i+1}$. 
  All other cases do not work.}
  \label{tab:test}
\end{table}

\end{proof}
The set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the rationals $\mathbb{Q}_{>1}$, which in turn are dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by a sequence $f_n := c2^n / (d2^n+1)$ with every element $f_n$ in the set $F$. \nick{can turn into lemma}

@@

\begin{theorem}
	Consider a general magic state distillation process that converts magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes n'}$ as well as equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes n'}$, where we assume that $W_{\tau^{\otimes n}}(\bmx) = a_{\bmx}/K$ and $W_{\tau'^{\otimes n'}}(\bmx) = a_{\bmx}/K$ for positive integers $a_{\bmx}, a_{\bmx}'$ and $K = \sum_{\bmx} a_{\bmx} = \sum_{\bmx} a_{\bmx}'$.  \nick{It may be more convenient to consider $W_{\tau}(\bmx') = a_{\bmx'}/K$, so that $K$ ends up raised to the power of $n$}

@@

	We have that 
\begin{equation}	
	\Big(W_{\rho_n}(\bmx), W_{\tau_n}(\bmx')\Big) \succ \Big(W_{\rho'_{n'}}(\bmx), W_{\tau'_{n'}}(\bmx')\Big)
\end{equation}	
or equivalently $\Gamma_{\bma}(W_{\rho_n}(\bmx)) \succ \Gamma_{\bma'}(W_{\rho'_{n'}}(\bmx))$ for all $\bmx$, where
\begin{align}
	\Gamma_{\bma}(W_{\rho_n}) &= \bigoplus_{\bmx} W_{\rho_n}(\bmx) \left(\frac{1}{KW_{\tau_n}(\bmx)}, \dots, \frac{1}{KW_{\tau_n}(\bmx)} \right)\nonumber\\
	&= \frac{1}{K}\bigoplus_{\bmx} \Big( W_{\rho_n|\tau_n}(\bmx), \dots, W_{\rho_n|\tau_n}(\bmx) \Big)
\end{align}
and similarly for $\Gamma_{\bma'}(W_{\rho'_{n'}})$.
Therefore,
\begin{align}
	&H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) = \frac{1}{1-\alpha} \log_2 \left( \frac{d^{2n}}{K^\alpha} \sum_{\bmx} \big[ W_{\rho_n|\tau_n}(\bmx) \big]^\alpha \right) = \nonumber\\
	&\frac{1}{1-\alpha} \log_2 \left( \frac{d^{2n}}{K^\alpha} \sum_{\bmx_1, \dots, \bmx_n} \big[ W_{\rho|\tau}(\bmx_1) \dots W_{\rho|\tau}(\bmx_n) \big]^\alpha \right)
\end{align}
while
\begin{equation}
	D(\rho||\tau) = \frac{1}{\alpha-1} \log_2 \sum_{\bmx} \frac{W_{\rho}(\bmx)^\alpha}{W_{\tau}(\bmx)^{\alpha-1}}.
\end{equation}
\nick{correct mistakes, bridge gaps}
\end{proof}
